### 2023-10-11 5.Conclusions/further.tex
No more weights constraints

>>>>

\subsection{Removing weight constraints}\label{subsec:noCons}

Removing the weights constraints is tricky since the the \ac{opAmp} is based on a verilog-A model (\cref{subsec:opamp}). Indeed, the model needs to be changed in order not to output voltages outside of the system's voltage range ($[0,v_{dd}]$). Once that is done, the \ac{opAmp} should behave more like a real one. The \acp{opAmp} should now be able to output a saturated signal.

However those saturated levels need to be added to the training of the weights. This can be done in Keras by creating a custom layer in the circuit that keeps the values within a the defined range ($[-9,9]$ for this thesis). The training will thus happen with the values being saturated as it would happen in the circuit.

This solution is not implemented in the circuit as the saturating signals might affect the real circuit. This is would allow the circuit to access a larger range of weights and make the training more performant.
